Finally Tagless, Partially Evaluated

### 2008-10-15 tagless/tagless-final.tex
add missing word and remove use of 'thus' twice in same sentence

This interpreter~|RCN| is fully polymorphic over the answer type,
using higher-rank polymorphism through OCaml record types.
To avoid this higher-rank polymorphism in the core language,
we could also define |RCN| as
a functor parameterized over
the answer type.
\begin{code}
module RCN(W: sig type w end) = struct
  type ('c,'sv,'dv) repr = ('sv -> W.w) -> W.w   ...
\end{code}
This alternative is more cumbersome to use because the functor
needs to applied once for each answer type, but it translates
to, for example, Standard ML\@, whose core language does not
support higher-rank polymorphism.

@@

module CPST(S: Symantics1)(W: sig type 'c dw end) = struct open W
  type 'c dint = 'c S.dint
  type 'c dbool = 'c S.dbool
  type ('c,'da,'db) darr =
    ('c, 'da, ('c, ('c, 'db, 'c dw) S.darr, 'c dw) S.darr) S.darr
  type ('c,'dv) repr =
    ('c, ('c, ('c, 'dv, 'c dw) S.darr, 'c dw) S.darr) S.repr   ...
\end{code}
Modified thus, |CPST| produces modules that match |Symantics1| and
thus can be not only evaluated or compiled but also transformed
using |CPST| again.  The accompanying source file |inco.ml| shows
the details, including one-pass CPS transformations in the
higher-order style of \citet{danvy-representing}.

>>>>

This interpreter~|RCN| is fully polymorphic over the answer type,
using higher-rank polymorphism through OCaml record types.
To avoid this higher-rank polymorphism in the core language,
we could also define |RCN| as
a functor parameterized over
the answer type.
\begin{code}
module RCN(W: sig type w end) = struct
  type ('c,'sv,'dv) repr = ('sv -> W.w) -> W.w   ...
\end{code}
This alternative is more cumbersome to use because the functor
needs to be applied once for each answer type, but it translates
to, for example, Standard ML\@, whose core language does not
support higher-rank polymorphism.

@@

module CPST(S: Symantics1)(W: sig type 'c dw end) = struct open W
  type 'c dint = 'c S.dint
  type 'c dbool = 'c S.dbool
  type ('c,'da,'db) darr =
    ('c, 'da, ('c, ('c, 'db, 'c dw) S.darr, 'c dw) S.darr) S.darr
  type ('c,'dv) repr =
    ('c, ('c, ('c, 'dv, 'c dw) S.darr, 'c dw) S.darr) S.repr   ...
\end{code}
Modified thus, |CPST| produces modules that match |Symantics1| and
can be not only evaluated or compiled but also transformed
using |CPST| again.  The accompanying source file |inco.ml| shows
the details, including one-pass CPS transformations in the
higher-order style of \citet{danvy-representing}.
